Matching bullets

### 2015-11-17 imaging-paper.Rnw

% Application

% Conclusion

>>>>

To improve upon the previous algorithm, the first step must be to eliminate the grooves from the images under the assumption that they do not contain relevant information for determining a match. Fortunately, the location and appearance of the grooves in these 2d plots is quite consistent. Because a bullet is scanned groove to groove, the groove should appear within approximately scan points from each end. That is, on y coordinate system ranging from 0 to 1000 as these images, are, the grooves will appear between $y \in \{0, 100\}$ and $y \in \{900, 1000\}$. Hence, the algorith for removing the grooves can be described as follows:

\begin{enumerate}
    \item Fix an x coordinate value.
    \item Remove values from $y \in \{0, 100\}$ and $y \in \{900, 1000\}$.
    \item For each y value from 100 to 900, compute a rolling average to smooth out any deviations occurring near the minimums.
    \item Determine the minimum in the first half (corresponding to the left groove) and the minimum in the right half (corresponding to the right groove)
    \item Remove all y values below the minimum and above the maximum
\end{enumerate}

Next, we fit a Loess regression to the data

<<loess_fit, echo=FALSE, fig.width=10, fig.height=7, out.width='\\linewidth', warning=FALSE, fig.cap='Loess fit for part 1 of bullet 1', fig.pos='H', message=FALSE>>=
br111 <- get_bullet(file.path("GitHub", "x3prproto", "images", "Hamby252_3DX3P1of2", "Br1 Bullet 1-1.x3p"))
br111.groove <- get_grooves(br111)

my.loess <- fit_loess(br111, br111.groove)

my.loess$fitted
@

<<loess_resid, echo=FALSE, fig.width=10, fig.height=7, out.width='\\linewidth', warning=FALSE, fig.cap='Loess fit residuals for part 1 of bullet 1', fig.pos='H'>>=
my.loess <- fit_loess(br111, br111.groove)

my.loess$resid
@

\section{Application}

\section{Conclusion}
